Developing a preprint culture in biology

### 2012-10-05 ms.tex
add Titus story

The first and most often discussed advantage of arXiv and open preprints is
speed (Figure~\ref{fig:map}). The time between submission and the official
publication of a manuscript can be measured in months, sometime in years. For
all this time, the research is known only to a select few: colleagues, editors,
reviewers. Thus, the science cannot be used, discussed, or reviewed by the
wider scientific community. This stage of manuscript preparation is a problem
for both scientists and publishers. Manuscripts that are unknown cannot be used
and thus take more time to be cited. It has been shown that high-energy physics,
with its high arXiv submission rate, had the highest immediacy among physics and
mathematics \cite{pra05}. Immediacy measures how quickly articles are cited.

>>>>

The first and most often discussed advantage of arXiv and open preprints is
speed (Figure~\ref{fig:map}). The time between submission and the official
publication of a manuscript can be measured in months, sometime in years. For
all this time, the research is known only to a select few: colleagues, editors,
reviewers. Thus, the science cannot be used, discussed, or reviewed by the wider
scientific community. In a recent blog post, C Titus Brown noted how posting a
paper on preprint lead to a quick citation (arXiv papers can be cited) and his
research was integrated by another researcher \cite{bro12}. The current system
of hiding manuscripts before acceptance pose problems for both scientists and
publishers. Manuscripts that are unknown cannot be used and thus take more time
to be cited. It has been shown that high-energy physics, with its high arXiv
submission rate, had the highest immediacy among physics and mathematics
\cite{pra05}. Immediacy measures how quickly articles are cited.
